An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-06 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

\begin{abstract}
There exist various methods and tools to size solar photovoltaic systems. The tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step do not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to output within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
\end{abstract}

@@

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

@@

Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design. The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance. This method do not the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.

@@

\subsection{Assumptions and Premises}
Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of every item of PV sizing. Data sheet from each item is necessary to collect the technical information. And the price of each item was collected using the internet (in US dollars).

@@

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) ????

>>>>

\begin{abstract}
There exist various methods and tools to size solar photovoltaic systems, however the tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step do not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to output within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
\end{abstract}

@@

Our work makes two major contributions. \textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. \textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

@@

Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design. The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance. This method do not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.

@@

\subsection{Assumptions and Premises}
Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect the technical information. Moreover, the price of each item was collected using the internet (in US dollars).

@@

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $105.06$ to $235.75$ minutes. Only case 7 presented a \textit{timeout} result.
The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}. %The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.

CBMC and ESBMC were not capable to produce some conclusive results. Situations of \textit{internal failure} or \textit{timeout} or \textit{out of memory} occurred; this partially answers the \textit{RQ2}. Worth to mention that the internal failure presented by the ESBMC verifier was a Z3 solver issue (a bug), and this will demand an updated version of the ESBMC.

Related to the HOMER Pro, xxx

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) the cost analysis is well tailored to the Amazon region of Brazil, however a broad analysis from other isolated areas must be performed in order to make the optimization general in terms of applicability.
